A Novel Failure Detection Solution with Multiple QoS in Data Center Networks

### 2016-07-05 SIG Proceedings Template-Jan2015 Zip/paper.tex
experiment data && paper first draft

\title{A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\numberofauthors{2}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Shanghai, China}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor
????\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Shanghai, China}\\
       \email{????@sjtu.edu.cn}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.
\maketitle

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

@@

%
%  Use this command to print the description
%
\printccsdesc

@@

\section{Introduction}
Data center is a pool of resources interconnected using a communication network, a broad range of services (e.g., Web search, data analytic, storage backup) are hosted on data centers. Data center networks play a pivotal role in data centers as they integrate various resources and connect hundreds of thousands devices together (e.g. routers, switches, servers). Due to the scale of data center networks, failures are common and hence automated failure detection can help reduce mean-time-to-recovery and service disruption.

However, failure detection in data center networks should not be simplex. On one hand, data center networks are reliable \cite{gill2011understanding} due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols. For about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability. On the other hand, many applications hosted on data centers have very strict timing constraints \cite{tomsic20152w}, they require failure detectors to provide quality of service (QoS) with quantitative timeliness guarantees.

Unfortunately, few researches have noticed QoS difference in failure detection in data center networks. Some researches on failure detection architecture such as \cite{felber1999failure} \cite{van1998gossip} \cite{gillen2007scalable} \cite{xu2012smart} \cite{xu2012smart} focus on scalable node or process failure detection in large scale distributed systems without considering underlying network topologies. Other failure detection approaches \cite{bahl2007towards} \cite{herodotou2014scalable} \cite{kandula2005shrink} treat all the network devices equally.

Having realized the limitations of existing work and also to address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices. including servers, top of rack switches and links between them

This paper makes the following contributions:
\begin{itemize}
  \item To the best of our knowledge, 
  \item 
  \item 
\end{itemize}

@@

\section{Related Work}
In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure detection in data center networks.

@@

Chen et al. proposed a FD that provides QoS \cite{chen2002quality}. It estimates the expected arrival time (EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages. EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process. \textit{Chen FD} can adjust current network condition and set the timeout threshold adaptively by referring to recent heartbeats. Bertier et al. proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}. Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output a continuous accrual failure value other than a binary value at any time which stands for the failure probability of the process.

\subsection{Failure Detection Architecture}
A failure detection architecture aims to provide the service of monitoring nodes in large scale distributed systems in a scalable way.
Roughly speaking, there are two kinds of architectures. The first one is hierarchical architecture \cite{felber1999failure}, all the nodes are partitioned into different groups, each group has a leader node. Within a group, the leader node is responsible for monitoring all the nodes. Leader nodes periodically send node status information of his group to other leader nodes. Hierarchical architecture can reduce the number of heartbeat messages effectively, but it exists \textit{Single Point of Failure} problem, when the leader node crashes, it needs to select a new leader.

@@

\subsection{Failure Detection in Networks}
Different from the work mentioned above, failure detection in networks should consider network topology and localize failure positions at IP layer. Gill et al. present the first large-scale survey on failures in data center networks \cite{gill2011understanding}.

Also, there exists a large body of work on applying statistical approaches to failure localization in networks. Sherlock \cite{bahl2007towards} localizes failures to limited network components by capturing dependencies between components. Shrink \cite{kandula2005shrink} leverages Bayesian Network model to diagnose root cause of IP network failures. Herodotou et al. \cite{herodotou2014scalable} actively inject ping traffic into network and analyze the ping results overlaid on top of the network topology. It will generate a ranked list containing the suspected failed device and links along with their failure score that can best explain the observed ping data.

@@

A data center is a facility used to house computer systems and associated components, it usually contains hundreds of thousands devices and links. Modern data centers use hierarchical architecture. Figure 1 depicts a conventional data center network architecture \cite{gill2011understanding, greenberg2009vl2, herodotou2014scalable}. At the bottom layer are racks of servers, typically there are 20 to 40 servers in each rack, and each server in the same rack connects to a Top of Rack (ToR) Switch via a 1 Gbps link. Each ToR then connects to a primary and a backup Aggregation Switch (AS) for redundancy. ASs are connected to Access Routers (ARs) forming a complete bipartite graph. Finally, ARs are connected to Core Routers (CRs).

To limit overheads and to isolate different services, servers are partitioned into virtual LANs (VLANs). All links in the data center use Ethernet as link layer protocol and physical connections are a mix of copper and fiber cables. In addition to the devices in Figure 1, there may exist other devices like load balancers (LBs) and firewalls.

Modern data center usually employs \textit{Equal Cost MultiPath} (ECMP) routing within the data center for fault tolerance, which means that there are multiple paths from source to destination. Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in ns-3.

% figure
\begin{figure}
\centering
\includegraphics{topology}
\caption{Conventional Data Center Network Topology}
\end{figure}

@@

Different network device should have different quality of service (QoS). Gill et al. \cite{gill2011understanding} have shown the diversity of different devices' failure characteristics. Unfortunately, none of the work in Section 2 treats these devices differently. We firstly divide network devices into two categories.

\begin{itemize}
\item \textbf{Imperative Device.} This category includes servers, ToRs and links between ToRs and servers. Typically servers run various user applications and store user data. The crash of servers may cause user-perceived faults. The crash of a ToR will make servers under it unreachable. Also Gill et al. declare that the downtime of ToRs may be very long. Thus the failure detection for these devices must be fast enough besides the accuracy requirement.

\item \textbf{Non-imperative Device.} It includes links, other routers and switches. A single failure of a link or a router does not affect the functionality of a data center because of path redundancy. So administrators care more about how effective the detect service is (The ability to identify actually happening failures).

@@

% figure
\begin{figure}
\centering
\includegraphics{system}
\caption{Failure Detection System Architecture}
\end{figure}

Figure 2 illustrates the entire architecture of our failure detection system. It mainly contains two modules. The servers failure detection system combines centralized with decentralized structures. A server can both play the role of a detector and a monitored object. Each server is monitored by multiple FD processes installed on different servers for redundancy. A server can also monitor a couple of servers. Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}. \textbf{Crash Decider} will determine the final status of this server.

@@

\section{Failure Detection Approach}
In this section, we will discuss the detailed design of different modules of the failure detection system respectively.

\subsection{K-detectors Model}
To detect the crash of servers and ToRs effectively and efficiently, this paper propose a detection model named $K$-detectors model. Our detection model is based on the assumption that once the server or ToR crashes, it never recovers by itself. The QoS of failure detection are as follows:

\begin{itemize}
\item \textbf{Efficiency.} It measures how fast the system can report the crash after it crashes. The system is more efficient if it takes less time to detect a failure.
\item \textbf{Completeness.} It measures whether the system can detect all the crashed objects. The system is more complete if it rules out fewer true crashed ones.
\item \textbf{Soundness.} In some scenarios, the behavior of the network may vary. For example, message loss and message delay may happen sometimes. The detection system should be sound enough to distinguish between such condition and a real crash.

@@

In $K$-detectors model, each server is monitored by $K$ FDs on different servers where $K$ is a parameter tuned by users. When a FD considers a server crashes, it sends a crash report message to \textbf{Crash Decider}. If the output of the FD transforms from suspect to trust, it re-sends a message to revoke the most recent crash report.

\begin{equation}
S_{s,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & |CRM_{s,t}|\geq\left\lfloor(K+1)/2\right\rfloor \\

    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $CRM_{s,t}$ denotes the collection of crash report messages for server $s$ until time $t$, $S_{s,t}$ denotes the status of server $s$ at time $t$. If \textbf{Crash Decider} receives $\left\lfloor(K+1)/2\right\rfloor$ crash messages of a server, it considers the server to have crashed.

\subsection{Monitoring Rule Inference}
To form the $K$-detectors model and also to meet QoS to the greatest extent, we propose the following specifications of monitoring relationships among servers:
\begin{enumerate}
    \item Each sever monitors $K$ servers. This balances monitor intensity of each server.
    \item A server cannot monitor itself.
    \item A server is monitored by $K$ different servers.
    \item $K-1$ of the $K$ detectors are on the servers at the same rack.
    \item The monitoring rule should ensure each link covered by heartbeat messages.
    \item Each rack monitors servers of other racks which vary from different racks averagely.
\end{enumerate}

\subsubsection*{Rationale}
\quad Intuitively, the use of $K$ FDs is able to adapt to bursty-traffic conditions like message loss because the determination of a failure requires at least $\left\lfloor(K+1)/2\right\rfloor$ FDs' agreement. Also, $K$-detectors can prevent crashes of FDs to some extent. Theoretically, a failure can still be detected even when $K-\left\lfloor(K+1)/2\right\rfloor=\left\lfloor K/2\right\rfloor$ of its detectors crashed.

@@

The last one is an extension of specification five. It is for the consideration of ToRs' detection, we will discuss it in detail in Section 5.4.

\subsection{FD Algorithm}
FD algorithm is used to decide the status of one monitored object by one FD. Our FD algorithm is almost the same as \textit{Chen} FD \cite{chen2002quality} except for some minor changes.

@@

After that, we utilize hyperbolic tangent function to model current suspicious level:

\begin{equation}
\tau(t_{now}) = |tanh(t_{now}-EA_{l+1})|
\end{equation}
suspicious level $\tau(t_{now})$ always ranges from 0 to 1, when $t_{now}$ grows bigger, the suspicious level is closer to 1, which implies a higher failure probability. A continuous valued rather than binary valued output decouples the interpretation of failure data from the failure monitoring mechanism, user applications can set their own threshold according to their demands.

\subsection{Failure Detection for ToRs}
Apart from determination of servers' crashes, \textbf{Crash Decider} is also responsible for failure detection for ToRs. If most or even all servers in a rack is reported crash by FDs of other racks, it is more likely that the top of rack switch crashes rather than the servers.

\begin{equation}
S_{ToR,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & | \{s | s \in ToR, \\
    && CRMO_{s,t} \not = \emptyset, \\
    && |CRM_{s,t}|=1\} | \geq \alpha \cdot m \\

    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR. $CRMO_{s,t}$ denotes the collection of crash report messages of $s$ coming from outside racks until time $t$. When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR. The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure. An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.

\subsubsection*{Upper Bound of $\alpha$}
Theoretically, a smaller $\alpha$ means a more aggressive detection. We can set an appropriate $\alpha$ empirically by looking back on historical data on ToR crashes. Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}:
\begin{equation}
    \begin{aligned}
        &m_0  = \frac{m}{n-1}(n-k_0) = \frac{m(n-k_0)}{n-1}\\
        &\alpha \leq \alpha_0  = \frac{m_0}{m} = \frac{n-k_0}{n-1}\\
        &\text{where } k_0 \text{ is the minimum of } k\\
        & s.t. \quad Pr(x\leq k) = \sum_{r=0}^k C_n^r p^r(1-p)^{n-r} \geq p_0 \\
    \end{aligned}
\end{equation}
$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$, $m_0$ is the number of observed crash report messages, it equals to number of alive ToRs times number of detectors per rack. Consequently, given $p$ and $p_0$, the theoretical upper bound of $\alpha$ should be $\alpha_0$.

To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm of \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i$ is an imperative device

        \FOR{$i \text{ in imperative devices}$}
            \STATE $S_{i,t_0} \leftarrow trust$
        \ENDFOR
	    \WHILE{$True$}
            \STATE $List<Integer> failsEachRack \leftarrow \emptyset$
            \FOR{each $i$ in Servers}
                \STATE $rackID \leftarrow getRackID(i)$
                \IF{$|CRM_{i,t_{now}}| \geq \left\lfloor(K+1)/2\right\rfloor$}
                    \STATE $S_{i,t_{now}} \leftarrow suspect$
                \ELSE
                    \STATE $S_{i,t_{now}} \leftarrow trust$
                    \IF{$\text{only one CRM coming from other rack}$}
                    \STATE $failsEachRack.get(rackID)\text{++}$
                    \ENDIF
                \ENDIF
            \ENDFOR

>>>>

\title{A Novel Failure Detection Solution with Multiple QoS in Data Center Networks }
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\numberofauthors{2}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Shanghai, China}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor
????\\
       \affaddr{????}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Shanghai, China}\\
       \email{????@sjtu.edu.cn}
}

\maketitle

\begin{abstract}
Large scale data center networks are complex due to hundreds of thousands devices and links in them. Failures of these devices and links sometimes can lead to user-perceived service interruptions. Thus automated failure detection plays a very important role in maintaining the reliability of data centers. Many researches have been performed on failure detection in networks or distributed systems, but few of them identifies quality of service (QoS) multiplicity of failure detection in data center networks.

In this paper, to tackle with this problem, we firstly divide network devices into two categories: imperative devices whose failures need to be detected in real time, and non-imperative devices. Subsequently, we leverage a co-detection approach named K-detectors to detect failures of imperative devices, while the key idea of non-imperative devices failure detection is to analyze network traffic changes over time.

We evaluate our approach on a simulated network built by ns-3. Experimental results show that for imperative devices, our approach has a better QoS except for limited detection time increase in the presence of normal message loss and different size of failures. For non-imperative devices, our approach outperform existing work in terms of accuracy and failure discrimination.
\end{abstract}

@@

%
%  Use this command to print the description
%
%\printccsdesc

@@

\section{Introduction}
Data center is a pool of resources interconnected using a communication network, a broad range of services (e.g., Web search, data analytic, storage backup) are hosted on data centers. Data center networks play a pivotal role in data centers as they integrate various resources and connect hundreds of thousands devices together (e.g. routers, switches, servers). For example, the Microsoft Live online services are supported by a Chicago-based
data center spanning more than 700,000 square feet \cite{DBLP:series/sbcs/LiuMVLH13}.

Due to the complexity and scale of data center networks, failures are common. Hence it is crucial to detect failures in the networks efficiently and effectively. Traditionally, domain experts are responsible for failure detection with the help of network monitoring data. But such a manual process is time-consuming, error-prone and not scalable. So automated failure detection approaches are useful in terms of helping reduce mean-time-to-recovery and service disruption.

However, failure detection in data center networks should not be simplex. On one hand, data center networks are reliable due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols. Evidence shows that for about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability \cite{gill2011understanding}. On the other hand, many applications hosted on data centers have very strict timing constraints \cite{tomsic20152w}, they require failure detectors to provide quality of service (QoS) with quantitative timeliness guarantees.

Unfortunately, few researches have noticed QoS difference in failure detection of data center networks. Some researches on failure detection architecture such as \cite{felber1999failure}\cite{van1998gossip}\cite{gillen2007scalable}\cite{xu2012smart}\cite{xu2012smart} focus on the scalability issue of process crash detection in large scale distributed systems without considering underlying network topologies, while other work on failure localization in data center networks such as \cite{bahl2007towards}\cite{herodotou2014scalable}\cite{kandula2005shrink} treat all the network devices equally and utilize a general detection approach.

To address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices. Imperative devices mainly include servers, top of rack switches and links between them, while non-imperative devices include other routers, switches and links. The main difference between them is that imperative devices have strict timing constraints of QoS as the failures of them may affect application functionalities. Naturally, our detection approach is two-fold: for imperative devices, we propose a co-detection model called K-detectors model to ensure the timeliness, soundness and accuracy at the same time. For non-imperative devices, we utilize a data mining based model to produce a ranked list consisting of suspect devices by extracting network traffic features. To evaluate our work, we compare our approach with hierarchical detection architecture \cite{felber1999failure} in terms of detection for imperative devices, and the work of Herodotou et al. \cite{herodotou2014scalable} in terms of detection for non-imperative devices. The experimental results prove the effectiveness of our work.

This paper makes the following contributions:
\begin{itemize}
  \item We identify the differences in QoS of failure detection in data center networks.
  \item We further divide network devices into two categories and propose effective failure detection approaches for these two kinds of devices respectively.
  \item We set up a series of evaluation metrics to evaluate different aspects of failure detection approaches.
  \item We implement our approach as well as other baselines on the same simulated data center network and prove the effectiveness of our approach.
\end{itemize}

@@

\section{Related Work}
In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure detection in networks.

@@

Chen et al. proposed a FD that provides QoS \cite{chen2002quality}. It estimates the expected arrival time (EAs) of the next heartbeat message according to a slide window storing $n$ most recent arrived messages. EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process. \textit{Chen FD} can adjust current network condition and set the timeout threshold adaptively by referring to recent heartbeats. Bertier et al. proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}. Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output a continuous accrual failure value rather than a binary value which stands for the failure probability of the process at any time.

\subsection{Failure Detection Architecture}
A failure detection architecture aims to provide the service of monitoring nodes in large scale distributed systems in a scalable way.
Roughly speaking, there are two kinds of architectures. The first one is hierarchical architecture \cite{felber1999failure}, all the nodes are partitioned into different groups, each group has a leader node. Within a group, the leader node is responsible for monitoring all the other nodes. Leader nodes periodically send node status information of his group to other leader nodes. Hierarchical architecture can reduce the number of heartbeat messages effectively, but it exists \textit{Single Point of Failure} problem, when the leader node crashes, it needs to select a new leader.

@@

\subsection{Failure Detection in Networks}
Different from the work mentioned above, failure detection in networks take network topology into consideration and localize failure positions at IP layer. Gill et al. present the first large-scale survey on failures in data center networks \cite{gill2011understanding}.

Also, there exists a large body of work on applying statistical approaches to failure localization in networks. \textit{Sherlock} \cite{bahl2007towards} localizes failures to limited network components by capturing dependencies between components. \textit{Shrink} \cite{kandula2005shrink} leverages Bayesian Network model to diagnose root cause of IP network failures. Herodotou et al. \cite{herodotou2014scalable} actively inject ping traffic into network and analyze the ping results overlaid on top of the network topology, it generates a ranked list containing the suspected failed device and links along with their failure score that can best explain the observed ping data.

% figure
\begin{figure}[t]
\centering
\includegraphics{topology}
\caption{Conventional Data Center Network Topology}
\end{figure}

@@

A data center is a facility used to house computer systems and associated components, it usually contains hundreds of thousands devices and links. Modern data centers use hierarchical architectures. Figure 1 depicts a conventional data center network architecture \cite{gill2011understanding}\cite{greenberg2009vl2}\cite{herodotou2014scalable}. At the bottom layer are racks of servers, typically there are 20 to 40 servers in each rack, and each server in the same rack connects to a Top of Rack (ToR) Switch via a 1 Gbps link. Each ToR then connects to a primary and a backup Aggregation Switch (AS) for redundancy. ASs are connected to Access Routers (ARs) forming a complete bipartite graph. Finally, ARs are connected to Core Routers (CRs). CRs are at the boundary of a data center network.

To limit overheads and also to isolate different services, servers are partitioned into virtual LANs (VLANs). All links in the data center use Ethernet as link layer protocol and physical connections are a mix of copper and fiber cables. In addition to the devices in Figure 1, there may exist other devices like Load Balancers (LBs) and Firewalls.

Modern data center usually employs \textit{Equal Cost MultiPath (ECMP)} routing within the data center for fault tolerance, which means that given a source and destination, there are multiple paths from the source to the destination. Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in ns-3.

@@

As we mentioned in Section 1, different network device should have different quality of service (QoS). Gill et al. \cite{gill2011understanding} have shown the diversity of different devices' failure characteristics. Unfortunately, none of the work in Section 2 treats these devices differently. We firstly divide network devices into two categories.

\begin{itemize}
\item \textbf{Imperative Device.} This category includes servers, ToRs and links between ToRs and servers. Typically servers run various user applications and store user data. The crash of servers may cause user-perceived faults. The crash of a ToR will make servers under it unreachable. Also Gill et al. declare that the downtime of ToRs may be very long. Thus the failure detection for these devices must be fast enough besides other requirements.

\item \textbf{Non-imperative Device.} It includes links, other routers and switches. A single failure of a link or a router does not affect the functionality of a data center because of built-in redundancy in data centers. So the data center administrators care more about whether the detection service is accurate enough to help them localize the real faults.

@@

% figure
\begin{figure}[t]
\centering
\includegraphics{system}
\caption{Failure Detection System Architecture}
\end{figure}

Figure 2 illustrates the entire architecture of our failure detection system. It mainly contains two modules. The upper half part illustrates the module for server failure detection. It is a combination of centralized and decentralized structures. A server can both play the role of a detector and a monitored object. Each server is monitored by multiple FD processes installed on different servers for redundancy. A server can also monitor a group of servers. Once a FD determines the crash of a server, it will send a crash report message to \textbf{Crash Decider}. \textbf{Crash Decider} will determine the final status of this server. On top of this, \textbf{Crash Decider} is also responsible for detecting ToR failures by combining all the server crash report messages together.

@@

\section{Failure Detection Approach}
In this section, we will discuss the detailed design of different aspects of the failure detection system respectively.

\subsection{K-detectors Model}
To detect the crash of servers and ToRs effectively and efficiently, this paper propose a co-detection model named $K$-detectors model. Our detection model is based on the assumption that once the server or ToR crashes, it never recovers by itself. We first refine the QoS of failure detection for servers:

\begin{itemize}
\item \textbf{Efficiency.} It measures how fast the system can report the crash after it crashes. The system is more efficient if it takes less time to detect a failure. In particular, server failures should be detected in real time.
\item \textbf{Completeness.} It measures whether the system can detect all the crashed objects. The system is more complete if it rules out fewer true crashed ones.
\item \textbf{Soundness.} In some scenarios, the behavior of the network may vary. For example, message loss and message delay may happen sometimes. The detection system should be sound enough to distinguish between such conditions and a real crash.

@@

In $K$-detectors model, each server is monitored by $K$ FDs on different servers where $K$ is a parameter tuned by user applications. When a FD considers a server crashes, it sends a crash report message to \textbf{Crash Decider}. If the output of the FD transforms from suspect to trust, it re-sends a message to revoke the most recent crash report.

\begin{equation}
S_{s,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & |\,CRM_{s,t}\,|\geq\left\lfloor(K+1)/2\right\rfloor \\

    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $CRM_{s,t}$ denotes the collection of crash report messages for server $s$ until time $t$, $S_{s,t}$ denotes the status of server $s$ at time $t$. If \textbf{Crash Decider} receives $\left\lfloor(K+1)/2\right\rfloor$ crash messages of a server, it considers the server to have crashed. So a server is still under monitor even when a number of its FDs crash.

\subsection{Monitoring Rule Inference}
A monitoring rule defines the monitoring relationships among a group of servers. To form the $K$-detectors model and also to meet QoS to the greatest extent, we propose the following specifications of a monitoring rule:
\begin{enumerate}
    \item Each sever monitors $K$ servers. This balances monitor intensity of each server.
    \item A server cannot monitor itself.
    \item A server is monitored by $K$ different servers.
    \item $K-1$ of the $K$ detectors are on the servers at the same rack.
    \item The monitoring rule should ensure each link covered by heartbeat messages.
    \item Each rack monitors servers of other racks which vary from different racks averagely.
\end{enumerate}

\subsubsection*{Rationale}
\quad Intuitively, the use of $K$ FDs is able to adapt to bursty-traffic conditions like message loss because the determination of a failure requires at least $\left\lfloor(K+1)/2\right\rfloor$ FDs' agreement. Also, $K$-detectors can prevent crashes of FDs to some extent. Theoretically, a failure can still be detected even when $K-\left\lfloor(K+1)/2\right\rfloor=\left\lfloor K/2\right\rfloor$ of its detectors crash.

@@

The last one is an extension of specification five. It is for the consideration of ToRs' failure detection, we will discuss it in detail in Section 5.4.

\subsection{FD Algorithm}
FD algorithm is used to decide the status of one monitored object by one FD. Our FD algorithm is almost the same as \textit{Chen FD} \cite{chen2002quality} except for some minor changes.

@@

After that, we utilize Hyperbolic Tangent Function to model current suspicious level:

\begin{equation}
\tau(t_{now}) = |\,tanh(t_{now}-EA_{l+1})\,|
\end{equation}
Hyperbolic Tangent Function is one of the widely used activation functions in neural networks. The suspicious level $\tau(t_{now})$ always ranges from 0 to 1, when $t_{now}$ grows bigger, the suspicious level is closer to 1, which implies a higher failure probability. A continuous valued rather than binary valued output decouples the interpretation of failure data from the failure monitoring mechanism, user applications can set their own threshold according to their demands.

\subsection{Failure Detection for ToRs}
Apart from determination of servers' crashes, \textbf{Crash Decider} is also responsible for failure detection for ToRs. The essential idea is that if most or even all servers in a rack is reported crash by FDs in other racks, it is more likely that the top of rack switch crashes rather than the servers.

\begin{equation}
S_{ToR,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & |\, \{s\, |\, s \in ToR, \\
    && CRMO_{s,t} \not = \emptyset, \\
    && |\,CRM_{s,t}\,|=1\} \,| \geq \alpha \cdot m \\

    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR. $CRMO_{s,t}$ denotes the collection of crash report messages of $s$ coming from outside racks until time $t$. When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR. The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure. Suppose there are $n$ racks in total, according to this specification, for each rack $r$, each other rack will monitor $m/(n-1)$ servers of rack $r$. An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.

\subsubsection*{Upper Bound of $\alpha$}
Theoretically, a smaller $\alpha$ means a more aggressive detection. We can set an appropriate $\alpha$ empirically by looking back on historical data on ToR crashes. Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}. When there are $k$ ToR crashes, the number of server crash report messages we can observe $m^\prime$ should be 
\begin{equation}
    m^\prime  = \frac{m}{n-1}(n-k) = \frac{m(n-k)}{n-1}
\end{equation}
Thus the value of $\alpha$ is at most:
\begin{equation}
    \alpha  = \frac{m^\prime}{m} = \frac{n-k}{n-1}
\end{equation}
Next, if given a confidence parameter $p_0$,
\begin{equation}
    \begin{aligned}
        &\alpha \leq \alpha_0  = \frac{m_0^\prime}{m} = \frac{n-k_0}{n-1}\\
        &\text{where } k_0 \text{ is the minimum of } k\\
        & s.t. \quad Pr(x\leq k) = \sum_{r=0}^k C_n^r p^r(1-p)^{n-r} \geq p_0 \\
    \end{aligned}
\end{equation}
$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$. Hence the theoretical upper bound of $\alpha$ is $\alpha_0$. Actually, because of server crashes, the number of crash report messages \textbf{Crash Decider} can receive may less than observe $m_0^\prime$, so the value of $\alpha$ should be less than its upper bound.

To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm of \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i \in \text{Imperative Device}$
